Programming Distributed Control Planes

### 2016-01-21 paper/introduction.tex
minor tweaks; technical work content missing

>>>>

It is well-known that network configuration is hard and error prone~\cite{x,y,z}; many studies of network incidents point to configuration errors as the leading cause.
%
One reason is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
%

Another, more fundamental reason is the semantic mismatch between intended policies and configuring individual devices.
%
Many policies are network-wide (e.g., such as prefer certain external neighbors over others, never announce certain destination prefixes externally, use a certain path only if another fails), but configurations describe the behavior of individual devices.
%
Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions produce the desired policy.
%
Ensuring policy-compliance through this manual decomposition is hard and error-prone, especially in the face of failures. Certain decompositions that work correctly otherwise, violate policies when failures occur.
%
As a result, many configuration errors manifest only during failures~\cite{batfish}.

To reduce configuration errors, the practitioner community is adopting a template-based approach~\cite{x,y}, in which common configuration constructs are captured as parameterized templates.
 While templates help with the low-level nature of configuration languages, they do not bridge the semantic divide between network policies and device-level configuration (\S\ref{sec:motivation}).

Software-defined networking (SDN) was, in part, the research community's response to the difficulty of maintaining policy compliance through distributed interaction of individual devices~\cite{xx}. It eliminates distributed control planes altogether. Instead of devices computing  forwarding tables through mutual interactions, they are told by a centralized controller exactly how to forward packets. The controller is responsible for ensuring policy compliance at all times. To program centralized control planes, researchers have developed increasingly sophisticated languages that let operators directly express network policies~\cite{x,y,z} that are then translated to forwarding tables at runtime.

However, SDN does not help the vast majority of networks in the world, which  still operate a distributed control plane. For the foreseeable future, many of these networks will continue to operate a distributed control plane, due to the difficulty of migration or the challenges that centralized control planes face in terms of scaling and failure robustness. 
%, scaling challenges of centralized control, or the inherent robustness of distributed control planes to failures.
%It is difficult to scale centralized control planes both 
Centralized control planes need careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.\footnote{For this challenge, researchers are exploring multi-controller networks, with interacting controllers, thus bringing back distributed control planes~\cite{x,y,z} and their current programming difficulties.}

In this paper, we ask if it is possible to centrally program distributed control planes.
Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations. The resulting forwarding behavior, which emerges through device interactions, must be policy-compliant even under failures.
If successful, this approach would combine easy programmability of centralized control planes and failure robustness of distributed control planes.

Through our system, called \sysname, we demonstrate the feasibility of centrally programming distributed control planes. We focus on BGP because it is a common and highly flexible way to implement such control planes.

\todo{new intro is not complete}

\todo{OLD TEXT IS BELOW}
